Sulfur Dioxide on Water's Surface

### 2011-04-05 Conclusions.tex
Finishing up the 2nd draft. Added new so2/h2o molecule cartoons, and a cartoon for the molecular layout near the interface for both systems.

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/angle-cartoons/system-surface.png}
		\caption{\wat~and \suldiox~both exhibit preferred orientations in the region near the liquid-gas interface. The neat-water system (A) with a single \suldiox~molecule (low-concentration) has surface waters orienting mostly flat to the interface. When the \suldiox~concentration is increased, as in the saturated system (B), the waters at the surface behave similar to the neat-water interface, but waters that venture into the adsorbed \suldiox~gas layer orient strongly with their bisectors pointing out from the aqueous phase towards the gas. In both cases, the \suldiox~orients with its molecular bisector pointing out to the gas phase when it is near the surface.}
		\label{fig:so2-surface-cartoon}
	\end{center}
\end{figure}

### 2011-04-05 EquilibratedOrientation.tex
Finishing up the 2nd draft. Added new so2/h2o molecule cartoons, and a cartoon for the molecular layout near the interface for both systems.

Although the plots show overall similarities for both the neat-water and saturated systems, the presence of a layer of adsorbed \suldiox~molecules alters the water orientation of the waters furthest from the aqueous bulk. The waters located above 0\angs~are further into the gas phase, and interact with the layer of adsorbed \suldiox~molecules. The \suldiox~layer does not provide the same amount of strong hydrogen bonding and solvation that the waters experience further in to the aqueous phase. The resulting orientation of waters above 0\angs, shown in the saturated plot of $\cos(\theta)$ of figure \ref{h2o-angles}, is with a bisector pointing further into the adsorbed \suldiox~gas layer, and both hydrogens pointing outward from the aqueous bulk. The effect is more pronounced further from the water phase, and above 5\angs~the $\cos(\theta)$ distribution is completely centered around $\cos(\theta)=+1$ (see figure \ref{water-angles}).

>>>>

Although the plots show overall similarities for both the neat-water and saturated systems, the presence of a layer of adsorbed \suldiox~molecules alters the water orientation of the waters furthest from the aqueous bulk. The waters located above 0\angs~are further into the gas phase, and interact with the layer of adsorbed \suldiox~molecules. The \suldiox~layer does not provide the same amount of strong hydrogen bonding and solvation that the waters experience further in to the aqueous phase. The resulting orientation of waters above 0\angs, shown in the saturated plot of $\cos(\theta)$ of figure \ref{fig:water-orientation}, is with a bisector pointing further into the adsorbed \suldiox~gas layer, and both hydrogens pointing outward from the aqueous bulk. The effect is more pronounced further from the water phase, and above 5\angs~the $\cos(\theta)$ distribution is completely centered around $\cos(\theta)=+1$ (see figure \ref{fig:water-angles}).
